\subsubsection{Sliding Window Simulation} \label{sliding_window_simulation}
A Sliding Window Simulation walks with a given window size and step size over the simulated acceleration time series
stream of an experimentee and tries to identify as many gestures as possible. The simulated acceleration time series
stream of an experimentee starts after the slide (j) of figure \ref{fig:slides} and ends in slide (r) of figure
\ref{fig:slides}. The Sliding Window Simulation is not able to read the labels of an gesture in the simulated
acceleration time series. Furthermore a Sliding Window Simulation gets the gestures of an experimentee from slide (b)
to (i) in figure \ref{fig:slides} as training data.

Such a simulation is not free of parameters. Two parameters have already been mentioned, the window size and the steps
size. In addition as parameters are the choice of the distance measure for time series, the threshold that marks
unclassifiable windows and the measure used for the Sliding Window Filter with a blur factor. All those parameters and
their options will be explained and mentioned in the following section. Furthermore a performance measure to compare the
different configured simulations will be explained.

\input{experiment/experimental_protocol/sliding_window_simulation/window_size_determination.tex}
\input{experiment/experimental_protocol/sliding_window_simulation/step_size_determination.tex}
\input{experiment/experimental_protocol/sliding_window_simulation/time_series_distance_measures.tex}
\input{experiment/experimental_protocol/sliding_window_simulation/threshold_determination.tex}
\input{experiment/experimental_protocol/sliding_window_simulation/sliding_window_filter_measures.tex}
\input{experiment/experimental_protocol/sliding_window_simulation/performance_measure.tex}
