\subsubsection{File Format} \label{file_format}
Interesting for the evaluation of the experiment are the acceleration data in three axis and the \textit{B} button down
and up events to mark the beginning and the end of a gesture. This results in three different kinds of events, incoming
acceleration data, the \textit{B} button is pressed down and the \textit{B} button is released up. The controller is
sending the acceleration data with an average gap of five milliseconds. Every event has been marked with the time
in milliseconds that have passed since the starting of the experiment. The representing line in a recorded file for a
acceleration data event is starting with the time in milliseconds followed by the acceleration data of all three axis.
The acceleration data of a axis is transfered as integer value with the unit decimetre per second squared. A \textit{B}
button down event is represented by a line also starting with the time in milliseconds followed by the keyword
\textit{START} and a counter for the gesture. The \textit{B} button up event is the same with the keyword \textit{END}
instead of \textit{START}. An example excerpt of a recorded file can look like the following.

\medskip
\noindent
{\it Example excerpt of a recorded file}
\begin{verbatim}
3045 20 19 74
3050 16 12 70
3055 START 1
3055 14 13 88
3060 0 11 76
\end{verbatim}
\noindent
{\small Line 1, 2, 4 and 5 are representations of acceleration data and line 3 marks the beginning of the first gesture
triggered by a \textit{B} button down event.}

\medskip

The recorded files are evaluated in section \ref{evaluation}. All
recorded files used in the evaluation are available on
GitHub\footnote{https://github.com/GordonLesti/SlidingWindowFilter-evaluator/tree/v1.0.1/src/main/resources}.
