\section{References}

\setbeamertemplate{bibliography item}[text]

\begin{frame}[allowframebreaks]{References}
    \begin{thebibliography}{1}
        \bibitem{batista2011complexity} Batista, Gustavo EAPA, Xiaoyue Wang, and Eamonn J. Keogh. "A complexity-invariant
            distance measure for time series." In Proceedings of the 2011 SIAM International Conference on Data Mining, pp.
            699-710. Society for Industrial and Applied Mathematics, 2011.
        \bibitem{chan1983algorithms} Chan, Tony F., Gene H. Golub, and Randall J. LeVeque. "Algorithms for computing the
            sample variance: Analysis and recommendations." The American Statistician 37, no. 3 (1983): 242-247.
        \bibitem{das1998rule} Das, Gautam, King-Ip Lin, Heikki Mannila, Gopal Renganathan, and Padhraic Smyth. "Rule
            Discovery from Time Series." In KDD, vol. 98, no. 1, pp. 16-22. 1998.
        \bibitem{ding2008querying} Ding, Hui, Goce Trajcevski, Peter Scheuermann, Xiaoyue Wang, and Eamonn Keogh. "Querying
            and mining of time series data: experimental comparison of representations and distance measures." Proceedings
            of the VLDB Endowment 1, no. 2 (2008): 1542-1552.
        \bibitem{keogh2002exact} Keogh, Eamonn. "Exact indexing of dynamic time warping." In Proceedings of the 28th
            international conference on Very Large Data Bases, pp. 406-417. VLDB Endowment, 2002.
        \bibitem{sakoe1978dynamic} Sakoe, Hiroaki, and Seibi Chiba. "Dynamic programming algorithm optimization for spoken
            word recognition." IEEE transactions on acoustics, speech, and signal processing 26, no. 1 (1978): 43-49.
        \bibitem{sart2010accelerating} Sart, Doruk, Abdullah Mueen, Walid Najjar, Eamonn Keogh, and Vit Niennattrakul.
            "Accelerating dynamic time warping subsequence search with GPUs and FPGAs." In Data Mining (ICDM), 2010 IEEE
            10th International Conference on, pp. 1001-1006. IEEE, 2010.
    \end{thebibliography}
\end{frame}
