\subsection{Recording}
A Wii Remote\texttrademark~Plus controller is able to observe acceleration data in three axis via sensors. Those
acceleration data plus all button events on the controller can be send via
Bluetooth\footnote{https://www.bluetooth.com/} to an other device. The other device was a computer that has executed the
recording software. Via a graphical user interface or shorten GUI the recording software instructed the experimentee to
perform gestures or physical activities. The experiment was a sequence of fullscreen slides that changed by performing a
gesture with the controller. Section \ref{protocol} explains the specific sequence of slides. The recording software
observed all acceleration data and \textit{B} button events during the hole experiment and saved it to a file. Marking
the beginning and the end of a gesture has been done with the \textit{B} button. The \textit{B} button is on the bottom
of the controller and works similar to a trigger from a gun.

The recording software has been implemented in Python\footnote{https://www.python.org/} and is available at
GitHub\footnote{https://github.com/GordonLesti/SlidingWindowFilter-experiment}. Main requirements for the recording
software are the open-source device driver for Nintendo Wii remotes,
xwiimote\footnote{https://github.com/dvdhrm/xwiimote} by David Herrmann and the language bindings for the xwiimote
package, xwiimote-bindings\footnote{https://github.com/dvdhrm/xwiimote-bindings} by Nicolas Adenis-Lamarre. The last
requirement was the main reason to implement the recording software in Python. For the GUI was choosen
TkInter\footnote{https://wiki.python.org/moin/TkInter}.

The first versin of the recording software had the major problem to control the GUI and the
processing of the Bluetooth data in one loop with a linear flow. That caused a stagnation in the Bluetooth data queue
while loading new images in the GUI. This problem could be solved by two communicating threads and a preloading of the
images. Unfortunately all until then existing records became unusable for the evaluation.

\input{experiment/recording/file_format.tex}
