\section{References}

\setbeamertemplate{bibliography item}[text]

\begin{frame}[allowframebreaks]{References}
    \begin{thebibliography}{11}
        \bibitem{acar2011mediaeval}
        E. Acar, S. Spiegel, and S. Albayrak.
        MediaEval 2011 Affect Task: Violent Scene Detection combining audio and visual Features with SVM.
        CEUR Workshop, 2011.

        \bibitem{batista2011complexity}
        G. Batista, X. Wang, and E. J. Keogh.
        A complexity-invariant distance measure for time series.
        ICDM, 2011.

        \bibitem{chan1983algorithms}
        T. F. Chan, G. H. Golub, and R. J. LeVeque.
        Algorithms for computing the sample variance: Analysis and recommendations.
        The American Statistician,1983.

        \bibitem{keogh2002exact}
        E. Keogh.
        Exact indexing of dynamic time warping.
        VLDB Endowment, 2002.

        \bibitem{lesti2017filter}
        G. Lesti and S. Spiegel.
        The sliding window filter for time series streams website.
        \url{https://gordonlesti.com/a-sliding-window-filter-for-time-series-streams/}

        \bibitem{liu2009uwave}
        J. Liu, L. Zhong, J. Wickramasuriya, and V. Vasudevan.
        uWave: Accelerometer-based personalized gesture recognition and its applications.
        PerCom, 2009.

        \bibitem{spiegel2015driving}
        S. Spiegel.
        Discovery of driving behavior patterns.
        Smart Information Systems - Advances in Computer Vision and Pattern Recognition, 2015.

        \bibitem{spiegel2015metering}
        S. Spiegel.
        Optimization of in-house energy demand.
        Smart Information Systems - Advances in Computer Vision and Pattern Recognition, 2015.
    \end{thebibliography}
\end{frame}
