\newpage
\begin{thebibliography}{2} \addcontentsline{toc}{section}{References}
    \normalsize
    
    \bibitem{acar2011mediaeval} 
    E. Acar, S. Spiegel, and S. Albayrak. 
    MediaEval 2011 Affect Task: Violent Scene Detection combining audio and visual Features with SVM. 
    Proceedings of CEUR Workshop, 2011.

    \bibitem{batista2011complexity} 
    G. Batista, X. Wang, and E. J. Keogh. 
    A complexity-invariant distance measure for time series. 
    Proceedings of the 2011 SIAM International Conference on Data Mining, pp. 699-710. Society for Industrial and Applied Mathematics, 2011.
        
    \bibitem{chan1983algorithms} 
    T. F. Chan, G. H. Golub, and R. J. LeVeque. 
    Algorithms for computing the sample variance: Analysis and recommendations.
	The American Statistician 37, no. 3 (1983): 242-247.
        
    \bibitem{das1998rule} 
    G. Das, K.-I. Lin, H. Mannila, G. Renganathan, and P. Smyth. 
    Rule Discovery from Time Series.
    In Proceedings KDD, vol. 98, no. 1, pp. 16-22. 1998.
        
    \bibitem{ding2008querying} 
    H. Ding, G. Trajcevski, P. Scheuermann, X. Wang, and E. Keogh. 
    Querying and mining of time series data: experimental comparison of representations and distance measures.
    Proceedings of the VLDB Endowment 1, no. 2 (2008): 1542-1552.
    
    \bibitem{itakura1975minimum} 
    F. Itakura. 
    Minimum prediction residual principle applied to speech recognition. 
    IEEE Transactions on Acoustics, Speech, and Signal Processing 23, no. 1 (1975): 67-72.

    \bibitem{keogh2002exact} 
    E. Keogh. 
    Exact indexing of dynamic time warping. 
    In Proceedings of the 28th international conference on Very Large Data Bases, pp. 406-417. VLDB Endowment, 2002.

    \bibitem{liu2009uwave} 
    J. Liu, L. Zhong, J. Wickramasuriya, and V. Vasudevan. 
    uWave: Accelerometer-based personalized gesture recognition and its applications. 
    Pervasive and Mobile Computing 5, no. 6 (2009): 657-675.

    \bibitem{sakoe1978dynamic} 
    H. Sakoe and S. Chiba. 
    Dynamic programming algorithm optimization for spoken word recognition.
    IEEE transactions on acoustics, speech, and signal processing 26, no. 1 (1978): 43-49.

    \bibitem{sart2010accelerating} 
    D. Sart, A. Mueen, W. Najjar, E. Keogh, and V. Niennattrakul.
	Accelerating dynamic time warping subsequence search with GPUs and FPGAs. 
	In Data Mining (ICDM), 2010 IEEE 10th International Conference on, pp. 1001-1006. IEEE, 2010.

    \bibitem{sokolova2009systematic} 
    M. Sokolova and G. Lapalme. 
    A systematic analysis of performance measures for classification tasks.
    Information Processing \& Management 45, no. 4 (2009): 427-437.
	
	\bibitem{spiegel2014lucky} 
	S. Spiegel, B.-J. Jain, and S. Albayrak. 
	Fast time series classification under lucky time warping distance. 
	In Proceedings of 29th Symposium on Applied Computing (SAC). ACM, 2014.

	\bibitem{spiegel2015driving} 
	S. Spiegel. 
	Discovery of driving behavior patterns. 
	In Smart Information Services - Computational Intelligence for Real-Life Applications, Advances in Computer Vision and Pattern Recognition, pages 
	315–343. Springer International Publishing Switzerland, March 2015.
	
	\bibitem{spiegel2015metering} 
	S. Spiegel. 
	Optimization of in-house energy demand. 
	In Smart Information Services - Computational Intelligence for Real-Life Applications, Advances in Computer Vision and Pattern Recognition, pages 	
	271–289. Springer International Publishing Switzerland, March 2015.
	
	\bibitem{spiegel2015diss} S. Spiegel. 
	Time series distance measures: segmentation, classification and clustering of temporal data. 
	Technische Universitaet Berlin (2015)
	
	\bibitem{xi2006fast} 
	X. Xi, E. Keogh, C. Shelton, L. Wei, C. A. Ratanamahatana.
	Fast time series classification using numerosity reduction. 
	In Proceedings of the 23rd international conference on Machine learning (pp. 1033-1040). ACM.           
	
\end{thebibliography}
